---
title: "Proj3Task1"
output: html_document
date: "2024-03-16"
---

Two plots with the f3 function:
first plot shows it being a softer curve

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# run this line once in the console to get the data4soils package
#devtools::install_github("byuidatascience/data4soils")

library(data4soils)

Ng <- cfbp_fpjuliet$ng
hist(Ng)
mean(Ng)
var(Ng)
```



# Two plots illustrating the parameters of f3

```{r}
l <- 1
l.2 <- 7
x <- seq(0,25,.01)

f3.1 <- function(x,l) {
  l * exp(-l * x)
}

y.1 <- f3.1(x,l)

y.2 <- f3.1(x,l.2)
  
plot(x, y.1, type="l", ylim=c(0,4))
```


When lambda is increased it goes higher.
this is the second plot:


``` {r}


plot(x, y.2, type="l", ylim=c(0,4))



```




## Visually fitted f2 Density histogram
this is a plot with a histogram and a curve 

``` {r}
x <- 7
l <- 9

gamma <- integrate(function(t) t^(x-1) * exp(-t), lower=0, upper=Inf)


f2 <- function(x, alpha, beta) {
  beta / alpha * gamma(alpha) * x^(alpha - 1) * exp(-beta * x)
}

hist(Ng, freq=FALSE)  # this set histogram to the probability
.33
#line(f2(gamma,x,l))  # It's saying that one of the parameters isn't a number(gamma?)
```

## Visually fitted f3 Density histogram 
this is the second  plot with a histogram and a curve :)

``` {r}
lambda <- .9
x <- seq(0,25,.1)
#might need to fix this later! 
f3 <- function(lambda, m) {
  return(lambda * exp(-lambda * m))
}

hist(Ng, freq=FALSE)
lines(x,f3(lambda,x))  # saying something about ... 
```





#I used rgamma() to simulate a sample of 25,000 measurements and used these to approximate the requested probability.


```{r}
set.seed(619)
beta <- 7.3
alpha <- .95
tmp2 <- rgamma(25000, shape = alpha, rate = beta)   # I think I need to look up and find in desmos
length(which(tmp2 > 10))

#Use the simulated sample to calculate the approximate probability that the amount of explosive in this sample will be more than 10 mg/kg?

#this simulates the sample
#RGAMMA() 

```




#I used rexp() to simulate a sample of 25,000 measurements and used these to approximate the requested probability.

REXP()
length(which(tmp3 > 10) / 25000
``` {R}
set.seed(619)
lambda <- .9
tmp3 <- rexp(25000, rate = lambda)
length(which(tmp3 > 10)) / 25000


# USE REXP() TO SIMULATE


```



#I verifiied my probability computations were correct using the Shiny App.
&
#I organized my work into a cohesive analysis.


